Phenomenological Robotics

### 2011-12-09 draft.tex
Reorganized introduction.

In the world of Good Old Fashioned Artificial Intelligence (GOFAI), scientists
attempted to fabricate intelligence by doing inference on symbolic
representations of the world. In Brooks \cite{brooks91} approach, this is done
by making agents respond to fixed isolable features of the environment.

Dreyfus \cite{dreyfus07} believes that the basis of human intelligence, coping
with everyday life, cannot be achieved by any of the approaches described above.
Instead, the fact that

@@

He points out that the pioneers in GOFAI learned, directly or indirectly, from
the philosophers. Hobbes' claim that reasoning was calculating and Descartes'
mental representations, among others, are cited as examples. At the same time,
he states that the critical insights formulated by existentialist philosophers,
such as Heidegger and Merleau-Ponty, were a sign that their enterprise was
comdemned to failure.

He criticizes Newell and Simon's claim that the mind could be understood as a
\emph{physical symbol system}, where streams of neuron pulses would be used as
symbols to represent the external world. Dreyfus points out that

>>>>

In the world of Good Old Fashioned Artificial Intelligence (GOFAI), scientists
attempted to fabricate intelligence by doing inference on symbolic
representations of the world.

Dreyfus~\cite{dreyfus07} points out that the pioneers in GOFAI learned, directly
or indirectly, from the philosophers. Hobbes' claim that reasoning was
calculating and Descartes' mental representations, among others, are cited as
examples. At the same time, he states that the critical insights formulated by
existentialist philosophers, such as Heidegger and Merleau-Ponty, were a sign
that their enterprise was comdemned to failure. He affirms that

% 1.?. On Brooks attempt. On Dreyfus believe on the failure of GOFAI and Brooks.

In Brooks' \cite{brooks91} approach, this is done by making agents respond to
fixed isolable features of the environment. Dreyfus \cite{dreyfus07} believes
that the basis of human intelligence, coping with everyday life, cannot be
achieved by any of the approaches described above. Instead, the fact that

@@
